plantecophys - an R package for analysing and modelling leaf gas exchange data

### 2015-09-09 manuscript.Rmd
Edited language section

## Language

The 'plantecophys' package is implemented in R, has no dependencies on other packages, and does not require compilation (i.e. it is written in native R only). As such it builds easily, and is highly portable. The source code is maintained with git version control, and is hosted in an online repository (http://www.bitbucket.org/remkoduursma/plantecophys). The repository includes an issue tracker, where users can suggest changes or report bugs.  This paper describes version `r packageVersion("plantecophys")` (git SHA `r cur_sha`).

\
All code used in this article (including the code to generate the actual article in markdown), can be downloaded (Zenodo link here).

>>>>

## Language and availability

The 'plantecophys' package is implemented in R, has no dependencies on other packages, and does not require compilation (i.e. it is written in native R only). As such it builds easily, and is highly portable. A stable release is available on CRAN. The source code is maintained with git version control, and is hosted in an online repository (http://www.bitbucket.org/remkoduursma/plantecophys). The repository includes an issue tracker, where users can suggest changes or report bugs.  This paper describes version `r packageVersion("plantecophys")` (git SHA `r cur_sha`).

\
All code used in this article (including the code to generate the actual article in markdown), can be downloaded from http://www.github.com/duursmaplantecophys2015.
